Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-02 src/tex/ms.tex
Fix minted path not showing up

Miles Cranmer would like to thank
the Simons Foundation for providing resources for pursuing this research;
Shirley Ho and David Spergel for countless insightful discussions about \pysr, feedback on this manuscript, promotion of it as a tool in the sciences, and for their support of this project;
my research collaborators who provided feedback throughout the development of \pysr, including Pablo Lemos, Peter Battaglia, Steve Brunton, Jay Wadekar, Paco Villaescusa-Navarro, Kaze Wong, Elaine Cui, Christina Kreisch, Nathan Kutz, Drummond Fielding, Keaton Burns, Dima Kochkov, Alvaro Sanchez-Gonzalez, Christian Jespersen, Patrick Kidger, Kyle Cranmer, Niall Jeffrey, Ana Maria Delgado, Keming Zhang, Pierre-Alexandre Kamienny, Michael Douglas, Francois Charton;
all of the wonderful open-source code contributors, including Mark Kittisopikul, T Coxon, Dhananjay Ashok, Johan Blåbäck, Julius Martensen, GitHub user \texttt{@ngam}, Christopher Rackauckas, Jerry Ling, Charles Fox, Johann Brehmer, Marius Millea, GitHub user \texttt{@Coba}, Pietro Monticone, Mateusz Kubica, GitHub user \texttt{@Jgmedina95}, Michael Abbott, Oscar Smith, and several others;
Marco Virgolin for extremely helpful comments on a draft of this paper, as well as general feedback;
Bill La Cava for providing feedback as well as spearheading the SRBench initiative, along with the rest of the SRBench organizers;
Brenden Petersen for feedback on \pysr as well as providing insights discussions about the SR landscape;
and so many others who have provided support to the project through email, Twitter, GitHub issues, and in-person.
I am blown away by the community that is forming around \pysr and the positive feedback it has received. Thank you.

>>>>

Miles Cranmer would like to thank
the Simons Foundation for providing resources for pursuing this research;
Shirley Ho and David Spergel for countless insightful discussions about \pysr, feedback on this manuscript, promotion of it as a tool in the sciences, and for their support of this project;
my research collaborators who provided feedback throughout the development of \pysr, including Pablo Lemos, Peter Battaglia, Steve Brunton, Jay Wadekar, Paco Villaescusa-Navarro, Kaze Wong, Elaine Cui, Christina Kreisch, Nathan Kutz, Drummond Fielding, Keaton Burns, Dima Kochkov, Alvaro Sanchez-Gonzalez, Christian Jespersen, Patrick Kidger, Kyle Cranmer, Niall Jeffrey, Ana Maria Delgado, Keming Zhang, Pierre-Alexandre Kamienny, Michael Douglas, Francois Charton;
all the wonderful open-source code contributors, including Mark Kittisopikul, T Coxon, Dhananjay Ashok, Johan Blåbäck, Julius Martensen, GitHub user \texttt{@ngam}, Christopher Rackauckas, Jerry Ling, Charles Fox, Johann Brehmer, Marius Millea, GitHub user \texttt{@Coba}, Pietro Monticone, Mateusz Kubica, GitHub user \texttt{@Jgmedina95}, Michael Abbott, Oscar Smith, and several others;
Marco Virgolin for extremely helpful comments on a draft of this paper, as well as general feedback;
Bill La Cava for providing feedback as well as spearheading the SRBench initiative, along with the rest of the SRBench organizers;
Brenden Petersen for feedback on \pysr as well as providing insights discussions about the SR landscape;
and so many others who have provided support to the project through email, Twitter, GitHub issues, and in-person.
I am blown away by the community that is forming around \pysr and the positive feedback it has received. Thank you.
